---
title: "Workshop Markdown"
author: "danS"
date: "18/02/2022"
output: html_document
---

```{r setup and packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)

```

# Report Summary

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data, include=FALSE}
gapminder_1997 <- read_csv("C:/Users/Dan/Desktop/un-report/data/gapminder_1997.csv")

nCountries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()

minGDP <- gapminder_1997 %>%
  summarize(round(min(gdpPercap))) %>%
  pull()

maxGDP <- gapminder_1997 %>%
  summarize(round(max(gdpPercap))) %>%
  pull()

```

```{r gdp_lifeexp_1997, echo=FALSE}

gapminder_1997%>%
  ggplot() +
  aes(x=gdpPercap, y=lifeExp, color=continent, size=pop/1000000)+
  geom_point()+
  labs(x="GDP Per Capita", y="Life Expectancy",
       title="Do people in wealthy countries live longer?", size="Population (in millions)")

```

## Graph
The above plot shows the relationship between GDP per capita and life expectancy
for a total of `r nCountries ` countries. For this set of countries,
economic wealth ranged from a minimum of USD `r minGDP`
to a maximum of USD `r maxGDP` per capita.

## Table

|Summary of Data|
|------|------|
|Number of Countries|`r nCountries`|
|Minimum GDP per capita|`r minGDP`|
|Maximum GDP per capita|`r maxGDP`|

## Others
[syntax cheatsheet](https://rmarkdown.rstudio.com/authoring_basics.html)

```{r ktable, echo=FALSE}

gapminder_1997 %>%
  filter(continent=='Oceania') %>%
  kable()

```
